An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-07-17 arxiv/poly-embed.tex
Fixing typo in acknowledgements annd Jessie's email

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro\\
 \texttt{jessica.finocchiaro@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}\\
 Microsoft Research, CU Boulder
}

@@

For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
Thus, $L^2$ embeds the loss $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ if $r_y = 1$ or $0$, and $0$ otherwise.
Observe that this is like $\elltop{2}$, with a punishment for reporting weight on elements of $r$ other than the outcome and a reward for showing a ``higher confidence'' in the correct outcome (i.e. $r_y = 2$).
Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.

@@

%\raf{ACKNOWLEDGEMENTS (commented out for submission)}
\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several import insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

>>>>

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro\\
 \texttt{jefi8453@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}\\
 Microsoft Research, CU Boulder
}

@@

For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
Observe that this is like $\elltop{2}$, with a punishment for reporting weight on elements of $r$ other than the outcome and a reward for showing a ``higher confidence'' in the correct outcome (i.e. $r_y = 2$).
Moreover, we can visually inspect the corresponding properties (Fig.~\ref{fig:top-k-simplices}) to immediately see why $L^2$ is inconsistent: for distributions where the two least likely labels are roughly equally (un)likely, the minimizer will put all weight on the most likely label, and thus fail to distinguish the other two.
More generally, $L^2$ cannot be consistent because the property it embeds does not ``refine'' (subdivide) the top-$k$ property, so not just $\psi$, but \emph{no} link function, could make $L^2$ consistent.

@@

%\raf{ACKNOWLEDGEMENTS (commented out for submission)}
\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

### 2019-07-17 neurips-19/poly-embed.tex
Fixing typo in acknowledgements annd Jessie's email

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessica Finocchiaro\raf{Jessie?} \\
 \texttt{jessica.finocchiaro@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo\\
 \texttt{bwag@colorado.edu}\\
 MSFT
}

@@

For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
Thus, $L^2$ embeds the loss $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ if $r_y = 1$ or $0$, and $0$ otherwise.
Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.

@@

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several import insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

>>>>

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro\raf{Jessie?} \\
 \texttt{jefi8453@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo\\
 \texttt{bwag@colorado.edu}\\
 MSFT
}

@@

For concreteness, consider the case with $k = 2$ over $n=3$ outcomes.
We can re-write $L^2(u)_y = \left(1 - u_y + \tfrac 1 2 (u_{[1]}+ u_{[2]} - \min(1,u_y))\right)_+$.
By inspection, we can derive the properties elicited by $\elltop{2}$ and $L^2$, respectively, which reveals that the set $\R'$ consisting of all permutations of $(1,0,0)$, $(1,1,0)$, and $(2,1,0)$, are always represented among the minimizers of $L^2$.
Thus, $L^2$ embeds the loss $\ell^2(r)_y = 0$ if $r_y = 2$ or $\ell^2(r)_y = 1 - r_y + \tfrac 1 2 \inprod{r}{\ones-e_y}$ otherwise.
Observe that $\ell^2$ is just $\elltop{2}$ with an extra term punishing weight on elements other than $y$, and a reward for a weight of 2 on $y$.

@@

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}
